%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.50in,top=0.6in,right=0.50in,bottom=0.6in]{geometry} % Document margins

\name{Rishi Vardhan K} % Your name
\address{github.com/rishivar \\ linkedin.com/in/rishi-vardhan} % Your address
\address{Tirunelveli \\ India} % Your secondary addess (optional)
\address{(+91)~$\cdot$~99440~$\cdot$~19244 \\ rishiharshavardhan@gmail.com \\ rishivardhan18126@cse.ssn.edu.in} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	ABOUT ME
%----------------------------------------------------------------------------------------

\begin{rSection}{About}

I am an Undergraduate Sophomore of Computer Science and Engineering interested in a career leaning with research. I am a highly motivated individual with interest towards Machine Learning and Computer Vision. 

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Sri Sivasubramaniya College Of Engineering} \hfill {\em Chennai} \\ 
B.E. in Computer Science \& Engineering  \hfill {\em August 2018 - Present} \\ 
Member of SSN Coding Community\\
Member of SSN Developers Community

{\bf Pushpalata Vidya Mandir} \hfill {\em Tirunelveli} \\ 
High School: Computer Science; CBSE; \hfill {\em March 2018 } \\ 
Elected to Inter-House Captain for School Politics in 2017 \\
Elected to President of Computer Club in 2016 \\
Elected to Inter-House Vice Captain for School Politics in 2016 \\
Class X 10 CGPA; Class XII 94.8\% (474/500)  

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Solarillion Foundation}{April 2020 - Present}{Undergraduate Teaching Assistant}{Chennai, India}
\item Currently working on automating the server applications by developing suitable bots for maintenance. 
\item Assisted new orientees on entry level python and machine learning assignments. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Solarillion Foundation}{September 2019 - Present}{Undergraduate Research Assistant}{Chennai, India}
\item Currently working on research dealing with adversarial impact on image deep learning models. 
\item Worked on predicting flight delay affected by historical flight performance and weather data. 
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, C, Java, Shell, C++, HTML, CSS, SQL \\
Machine Learning & scikit-learn, Keras, Tensorflow \\
Frameworks & Pandas, Simple-Transformers, Numpy, Git  \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects \& Research}


\begin{rSubsection}{Named Entity Recognition Model on Chemical Report Data}{April 2020 - Present}{Task 1 and Task 2, ChemU Lab, CLEF - 2020}{Chennai, India}
\item Working on implementing transformers approach to solve a named entity task. 
\end{rSubsection}

\begin{rSubsection}{Multi Label Classification model on Medical codes corpus}{February 2020 - May 2020}{Task 1 and Task 2, eHealth Lab, CLEF - 2020}{Chennai, India}
\item Implemented Transformers Approach to classify medical documents on  ICD10-CM and ICD10-PCS codes
\item Models worked on were BioBert, XLNet, Electra. 
\end{rSubsection}

\begin{rSubsection}{Majority Voting approach to Text Classification}{October 2019 - February 2020}{SemEval 2020 Task 4 Common Sense Validation and Explanation}{Chennai, India}
\item Worked on developing a majority voting classifier over BERT, XLNet and MicroTC to predict relevance on common-sense data.
\item Generated Text on context of common sense with Neural Machine Translation Model (NMT). 
\end{rSubsection}

\begin{rSubsection}{Early Risk Prediction model on Reddit users data}{March 2020 - May 2020}{Task 1 and Task 3, eRisk Lab, CLEF - 2020}{Chennai, India}
\item Developed a binary text classification model over Reddit users data to predict the chance and amount of probability that a user is susceptible to risk of self harm.
\item Models worked on were AdaBoost, Extra Trees, Gradient Boosting, Bernoulli Naive Bytes and CNN.
\end{rSubsection}




\begin{rSubsection}{Flight Delay Prediction}{September 2019 - December 2019}{Classification and Regression Model, Solarillion}{Chennai, India}
\item Worked on developing a Machine Learning model to predict whether a flight will be delayed or not and the amount of delay if occured.
\item A pipeline model from Classification to Regression was developed on consideration of historical flight performance and weather data. 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{Courses and Certification}

\item{\textbf{Machine Learning}} - Stanford Course on Coursera 
\item{\textbf{Convolutional Neural Networks for Visual Recognition}} - Stanford CS231n
\item{\textbf{Web Development}} - Frontend Web Development Course on Udemy
\item{\textbf{Android App Development}} - Android App Developer Course on Udemy
\item{\textbf{Computer Hardware}} - NIIT A+
\item{\textbf{Computer Networking}} - NIIT N+
\item{\textbf{University Courses}} - Python Programming, C Programming, Discrete Mathematics, Design and Analysis of Algorithms, Data Structures, Database Management Systems, Operating Systems, Computer Organisation and Architecture

\end{rSection}

\begin{rSection}{Accomplishments}

\item{\textbf{CBSE Regional Model Making Competition}} - Represented high school under the eco-safety category.
\item{\textbf{Agni Model Making Competition}} - Won the district level model making competition under Smart Technology category. 



\end{rSection}

\begin{rSection}{Extra Curricular Activities}

\item{\textbf{NSS}} - Involved in various community cleaning, awareness workshop activities concerning NSS Community.

\item{\textbf{Science Exhibition}} - Organised a 3D theatre viewing experience on the context of flora and fauna awareness in high school.  

\end{rSection}

\end{document}
